### 2021-03-22 Chapter-1/Chapter-1.tex
Updates from Overleaf

\chapter{Introduction} \label{chapter1}

Side-channels are ubiquitous in modern computer systems as sensitive information may be leaked through many kinds of negligent behaviors, such as power, electromagnetic radiation, or even sound~\cite{agrawal2002side,kar20178,chari1999towards,217605,genkin2014rsa}. It is typically hard to fix all side-channel vulnerabilities for real-world software systems.

Among them, address-based side channel attacks, such as cache attacks, memory page attacks, and controlled-channel attacks, are especially common and have been studied for years~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}. These
attacks result from vulnerable software and shared hardware components.
By observing program outputs or hardware behaviors, attackers can infer program
execution flows that manipulate secrets and guess secrets such as encryption
keys~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}.

In this chapter, we first introduce two code patterns that can be exploited to retrieve sensitive information. After that, we discuss some common attacks and corresponding defense strategies. The limitations of existing work motivate the research in the dissertation. Finally, we summarize the contributions of the dissertation.

>>>>

\chapter{Introduction} \label{chapter1}
Side channels are ubiquitous in modern computer systems as sensitive
information can leak through many mechanisms such as power,
electromagnetic radiation, and even sound~\cite{agrawal2002side,kar20178,chari1999towards,217605,genkin2014rsa}.
It is typically hard to fix all side-channel vulnerabilities for real-world software systems.

Among them, software side-channel attacks, such as cache attacks, memory page
attacks, and controlled-channel attacks, are especially problematic as they do not require physical proximity~\cite{7163052,217543,217589,lee2017inferring,191010,liu2015last}. These attacks arises from shared micro-architectural components in a computer processor.
By observing inadvertent interactions between two programs, attackers can infer program execution flows that manipulate secrets and guess secrets such as encryption keys~\cite{Osvik2006,Gullasch:2011:CGB:2006077.2006784,203878,10.1007/978-3-540-45238-6_6}.

Many side-channel attacks originate in two code patterns: data flow from secrets to load addresses and data flow from secrets to branch conditions. We refer to them as secret-dependent data accesses and control flows, respectively.

Recent work~\cite{203878,217537,Wichelmann:2018:MFF:3274694.3274741,Brotzman19Casym,236338,182946} can detect many side-channel vulnerabilities. For example, DATA~\cite{217537} reports 2,248 potential leakage sites for the RSA
implementation in OpenSSL 1.1.0f\@. 
Further analysis shows 1,510 leaks can be dismissed. But that
leaves 460 data-access leaks and 278 control-flow leaks. 
Many of these vulnerabilities have not been fixed by developers for a variety of reasons.

First, some vulnerable implementations perform better. For example,
RSA implementations usually adopt the CRT optimization,
which is faster but vulnerable to fault attacks~\cite{aumuller2002fault}.
Second, fixing vulnerabilities can introduce new 
weaknesses. Third, most vulnerabilities pose a negligible risk. 
Although some vulnerabilities result in the key being 
entirely compromised~\cite{184415, aumuller2002fault}, 
many others are less severe in reality. Therefore, we need a proper quantification metric to  assess the sensitivity of side-channel vulnerabilities, so a developer can efficiently triage them.

Previous work~\cite{182946,5207642} can identify numerous leakages or even provide an upper bound on the amount of leakage, which is useful to verify that an implementation is secure if it incurs zero leakage.
However, these techniques cannot quantify the severity of a leak because they over approximate the leakage. For example, CacheAudit~\cite{182946} 
reports that the upper-bound leakage of AES-128 exceeds the original key size. Besides, existing side-channel quantification work~\cite{182946,5207642} assumes an attacker runs the target program multiple times with different
input secrets and calculates an ``average'' estimation, which is different from real attack scenarios when the secret that an attacker wants to retrieve is fixed. As a consequence, those results are less useful to assess the severity level of each leakage site.
